Jug: Software for Reproducible Computation

### 2012-02-23 paper.tex
TXT Cite similar tools

\citet{Fomel2007} proposed a system built on top of Scons which shared
superficially similar design. Scons, like Make, is a build system. It supports
spawning parallel jobs using multiple threads. In the original use case, the
tasks are delegated to other commands and the operating system can take care of
parallelism. If, however, the tasks are computationally intensive in Python,
contention for the global interpreter lock will limit the amount of real
parallelism.\footnote{In the most commonly used Python interpreters, there is a
lock that prevents more than one thread from simultaneously executing
interpreted code, although they can execute non-interpreted code, as calling an
external programme or certain external libraries.}

>>>>

\citet{Fomel2007} proposed a system built on top of Scons which shared
superficially similar design. Scons, like Make, is a build system. It supports
spawning parallel jobs using multiple threads. In the original use case, the
tasks are delegated to other commands and the operating system can take care of
parallelism. If, however, the tasks are computationally intensive in Python,
contention for the global interpreter lock will limit the amount of real
parallelism.\footnote{In the most commonly used Python interpreters, there is a
lock that prevents more than one thread from simultaneously executing
interpreted code, although they can execute non-interpreted code, as calling an
external programme or certain external libraries.} Ruffus is another
Python-based solution which supports parallel execution of pipelines
\citep{Goodstadt16092010}. There is a strong dependency on the filesystem,
which makes its use very different from jug usage, which strives to make its
usage similar to straight Python usage. Using the Ruby programming language,
\citet{mishima2011} proposed Pwrake.
